\documentclass[a4paper,10pt]{article}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{cite}
\usepackage[table]{xcolor}
%used to not have a new page when including another .tex file
\usepackage{newclude}
%used to indent the first line in each section
\usepackage{indentfirst}

%
\begin{document}
%
    \title{Traffic Modeling with Unity 3D}

    \author{
    
    Isaiah Martinez \\ CSUN \\ Computer Science Department \\ isaiah.martinez.891@my.csun.edu
    
    \and
    
    Jae Molina \\ CSUN \\ Computer Science Department \\ jae.molina.499@my.csun.edu
    
    \and
    
    Anastasia Naydina \\ CSUN \\ Computer Science Department \\ anastasia.naydina.947@my.csun.edu
    
    }
          
    \date{02/19/2021}

    \maketitle
   
    \tableofcontents
 
    \newpage

    \section{Change History}

    Version: 0.09

    Modifier: Isaiah Martinez, Jae Molina, Anastasia Naydina
    
    Date: 2/19/24
    
    Description of Change: Discussed High Level Architecture of the project: Unity for modeling, C\#/Python for helper script, Python for ML training, and JS for API connectivity.
    Added template to follow for documentation.
    Structured git repo directories.
    First, we will be working on a set amount of locations with small amount of available traffic data.
    Later, we hope to implement API connectivity to obtain traffic info and map data with more locations.
 
    %horizontal line
    \noindent\rule{12cm}{0.4pt}

    Version: 0.05

    Modifier: Isaiah Martinez, Jae Molina, Anastasia Naydina
    
    Date: 2/12/24
    
    Description of Change: Made Git repository. 
    Looked at scholarly articles for related works.
    Uploaded sample scholarly article to view.
    Laid out big ideas for project.
    Began work on models to be used in Unity.

    \include*{progress}

    \include*{challenges}

\end{document}