\section{Design Goals}
\subsection{Purpose}
The purpose of this software project is to create a simulation within Unity to recreate real-time traffic scenarios. By focusing on real-time traffic data collection, different pathfinding algorithms, with visualization help of Unity, the project aims to provide users with a platform for comparing simulated traffic behaviors to real-life situations.
\subsection{Objectives}
Our initial goals for the project included:

\begin{enumerate}
	\item Real-Time Traffic Data Collection:
	Collect real-time data from satellite imagery to construct maps for the simulation.
	\item Pathfinding:
	Implementing pathfinding algorithms to simulate realistic vehicle movements and route optimization within the traffic simulation.
	\item Rendering in Unity with 3D Objects:
	Utilizing Unity's to create visual representations of the simulated traffic scenarios.
\end{enumerate}
\textbf{ Were they met? Why/Why not?}

Due to the project's complexity and time constraints, some of our initial goals were not fully met
\begin{enumerate}
	\item Real-Time Creation of Map with Data: While we did integrate real-time data collection mechanisms, such as traffic APIs through TomTom, into the project, the process of dynamically constructing maps within the simulation environment proved more challenging than originally believed. As a result, the maps were often pre-generated and simplified representations rather than real-time creations.
	\item Real-Time Comparison to Traffic: Achieving real-time comparison to real-life traffic was a significant challenge. Despite implementing a pathfinding algorithm and system, accurately recreating the complexities of real-world traffic behaviors within the Unity environment proved to be beyond the project's scope within the given timeframe.
	\item Different Pathfinding Algorithms: While we implemented several pathfinding algorithms, such as Dijkstra's algorithm and A* search, integrating a wide range of algorithms for comparative analysis was not feasible within the project's constraints.
\end{enumerate}
\textbf{Comparison to Initial Vision}
Despite falling short, the finished project represents a significant achievement in terms of simulating real-time traffic within a Unity. While compromises were made due to complexity and time constraints, the project still provides valuable insights into traffic simulation and serves as a foundation for future developments to the project.
