\documentclass[a4paper,10pt]{article}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage[table]{xcolor}
%used to not have a new page when including another .tex file
\usepackage{newclude}
\usepackage{hyperref}

%
\begin{document}
%
\title{3D Traffic Modeling in Unity}



	\author{
	Group 2:\\\\
	\textbf{Isaiah Martinez} \\ CSUN \\ Computer Science Department \\ isaiah.martinez.891@my.csun.edu \\
	\and
	\textbf{Jae Molina} \\ CSUN \\ Computer Science Department \\ jae.molina.499@my.csun.edu \\
	\and
	\textbf{Anastasia Naydina} \\ CSUN \\ Computer Science Department \\ anastasia.naydina.947@my.csun.edu
	}

          
    \date{05/13/2024}

    \maketitle
    
    \newpage
   
    \tableofcontents
 
    \newpage
    
    \include*{ChangeHist}

    \include*{Intro}

    \include*{DesGoal}

    \include*{SysBehav}

    \include*{LogView}

    \include*{SceneView}

    \newpage

    \begin{thebibliography}{}

        \bibitem{CNN} A. L. CNN Illustrations by Natalie Leung, ``Los Angeles' traffic problem in graphics,'' CNN, Feb. 27, 2018. \href{https://www.cnn.com/2018/02/27/americas/los-angeles-traffic/index.html}{Link}

        \bibitem{TraffApps} “The 7 Best Traffic Apps of 2023,” Lifewire. \href{https://www.lifewire.com/best-traffic-apps-4570916}{Link}

        \bibitem{TrafficPaper} Teo Niemirepo, J. Toivonen, Marko Viitanen, and J. Vanne, “Open-Source CiThruS Simulation Environment for Real-Time 360-Degree Traffic Imaging,” Nov. 2019, doi: https://doi.org/10.1109/iccve45908.2019.8965242.

        \bibitem{AITrackmania} “Training an unbeatable AI in Trackmania,” www.youtube.com. \href{https://www.youtube.com/watch?v=Dw3BZ6O_8LY}{Youtube Link}

        \bibitem{MLAgents} U. Technologies, “Make a more engaging game w/ ML-Agents | Machine learning bots for game development | Reinforcement learning | Unity,” unity.com. \href{https://unity.com/products/machine-learning-agents}{Link}

        \bibitem{EasyRoads} “EasyRoads3D Free v3 | 3D Characters | Unity Asset Store,” assetstore.unity.com. \href{https://assetstore.unity.com/packages/3d/characters/easyroads3d-free-v3-987}{Unity Store Link}

        \bibitem{TomTom} “Traffic APIs,” TomTom. \href{https://www.tomtom.com/products/traffic-apis/}{Link}.

        \bibitem{ConversionTomTom} “Zoom Levels and Tile Grid | Map Display API,” developer.tomtom.com. \href{https://developer.tomtom.com/map-display-api/documentation/zoom-levels-and-tile-grid}{Link}.

        \bibitem{HeightCalcTomTom} “Hillshade Tile | Map Display API,” developer.tomtom.com. \href{https://developer.tomtom.com/map-display-api/documentation/raster/hillshade-tile}{Link}.

    \end{thebibliography}

\end{document}